Structured Versus Decorated Cospans

### 2020-11-17 cospans.tex
Update cospans.tex

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

We also have that the monoidal unit of $F\lCsp_1$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\A$};
\node (B) at (1,0) {$1_\A$};
\node (C) at (2,0) {$1_\A$};
\node (D) at (1,-0.5) {$!_{1_\A} \in F(1_\A)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
\end{tikzpicture}
\]
where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$H(1_\A)$};
\node (B) at (1,0) {$H(1_\A)$};
\node (C) at (2,0) {$H(1_\A)$};
%\node (E) at (3,0) {$=$};
%\node (F) at (4,0) {$1_\mathsf{A'}$};
%\node (G) at (5,0) {$1_\mathsf{A'}$};
%\node (H) at (6,0) {$1_\mathsf{A'}$};
%\node (I) at (5,-0.5) {$!_{1_{\mathsf{A'}}} \in F'(1_{\mathsf{A'}})$};
\node (D) at (1,-0.5) {$\theta_{1_\A}E(!_{1_\A}) \phi \in F'(H(1_\A))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B);
%(F) edge node[above]{$1$} (G)
%(H) edge node[above]{$1$} (G);
\end{tikzpicture}
\]
as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \mathbb{H}(1_{F\lCsp_1})$$ 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$1_{\mathsf{A'}}$};
\node (A') at (0,-0.5) {$H(1_\A)$};
\node (B) at (1.5,0.5) {$1_{\mathsf{A'}}$};
\node (C) at (3,0.5) {$1_{\mathsf{A'}}$};
\node (C') at (3,-0.5) {$H(1_\A)$};
\node (D) at (1.5,-0.5) {$H(1_\A)$};
\node (E) at (5,0.5) {$!_{1_\mathsf{A'}} \in F'(1_\mathsf{A'})$};
\node (F) at (5,-0.5) {$\theta_{1_\A} E(!_{1_\A}) \phi \in F'(H(1_\A))$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$1$} (B)
(C) edge node[above]{$1$} (B)
(A) edge node[left]{$\kappa$} (A')
(C) edge node[right]{$\kappa$} (C')
(A') edge node [above]{$1$} (D)
(C') edge node [above]{$1$} (D)
(B) edge node [left] {$\kappa$} (D);
\end{tikzpicture}
\]
together with the morphism $\tau_\mu \maps F'(\kappa)(!_{1_\mathsf{A'}}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F'(H(1_\A))$. The following square then commutes for any horizontal 1-cell $M$ of $F \lCsp$: 
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$1_\mathsf{A'} \otimes \mathbb{H}(M)$};
\node (B) at (2.5,0) {$\mathbb{H}(1_\A) \otimes \mathbb{H}(M)$};
\node (C) at (0,-1) {$\mathbb{H}(M)$};
\node (D) at (2.5,-1) {$\mathbb{H}(1_\A \otimes M)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\mu \otimes 1$} (B)
(A) edge node[left]{$\ell$} (C)
(B) edge node[right]{$\mu_{1_\mathrm{A},M}$} (D)
(D) edge node[above]{$\mathbb{H}(\ell')$} (C);
\end{tikzpicture}
\]
where we have abbreviated the monoidal units of $F\lCsp_1$ and $F'\lCsp_1$ as $1_\A$ and $1_\mathsf{A'}$, respectively. The diagram of corresponding decorations is given by:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$};
\node (B) at (0,-0.5) {$d_{\mathbb{H}(M)}$};
\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\mathbb{H}(1_\A)}}\otimes d_{\mathbb{H}(M)})$};
\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\mathbb{H}(1_\A \otimes M)})$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[left]{$\tau_\ell$} (B)
(A) edge node[above]{$F'(H(\ell')\kappa)(\tau_{\mu \otimes 1})$} (A')
(A') edge node [right]{$F'(H(\ell'))(\tau_\kappa)$} (B')
(B') edge node [above] {$\tau_{H(\ell')}$} (B);
\end{tikzpicture}
\]
where $$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes. The other square involving the right unitors $r$ and $r'$ is similar. Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.

>>>>

On the other hand, the image of $M_1$ and $M_2$ is given by $\lH(M_1)$ and $\lH(M_2)$:

@@

\node (D) at (1.5,-0.5) {$d_{\lH(M_1)} = \theta_{c_1}E(d_{M_1})\phi \in F'(H(c_1))$};

@@

\node (H) at (6,-0.5) {$d_{\lH(M_2)} = \theta_{c_2}E(d_{M_2})\phi \in F'(H(c_2))$};

@@

and their tensor product $\lH(M_1) \otimes \lH(M_2)$ is given by:

@@

\node (D) at (2.5,-0.5) {$d_{\lH(M_1) \otimes \lH(M_2)} \in F'(H(c_1)+H(c_2))$};

@@

$$\hspace{-.4in} \scriptstyle{d_{\lH(M_1) \otimes \lH(M_2)} \maps 1 \xrightarrow{(\phi \times \phi)(\lambda^{-1} \times \lambda^{-1})} E(1) \times E(1) \xrightarrow{(\theta_{c_1} \times \theta_{c_2})(E(d_{M_1}) \times E(d_{M_2}))} F'(H(c_1)) \times F'(H(c_2)) \xrightarrow{\Phi_{H(c_1),H(c_2)}} F' (H(c_1)+H(c_2)).}$$  We then have a natural 2-isomorphism $\mu_{M_1,M_2} \maps \lH(M_1) \otimes \lH(M_2) \to \lH(M_1 \otimes M_2)$ in $F'\lCsp$ given by:

@@

\node (E) at (2.5,1) {$d_{\lH(M_1) \otimes \lH(M_2)} \in F'(H(c_1)+H(c_2))$};
\node (F) at (2.5,-1) {$d_{\lH(M_1 \otimes M_2)} \in F'(H(c_1+c_2))$};

@@

$$\tau_\kappa \maps F'(\kappa)(d_{\lH(M_1) \otimes \lH(M_2)}) \to d_{\lH(M_1 \otimes M_2)}$$

@@

\node (A) at (0,0.5) {$(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)$};
\node (B) at (0,-0.5) {$\lH(M_1 \otimes M_2) \otimes \lH(M_3)$};
\node (C) at (0,-1.5) {$\lH((M_1 \otimes M_2) \otimes M_3)$};
\node (A') at (4,0.5) {$\lH(M_1) \otimes (\lH(M_2) \otimes \lH(M_3))$};
\node (B') at (4,-0.5) {$\lH(M_1) \otimes \lH(M_2 \otimes M_3)$};
\node (C') at (4,-1.5) {$\lH(M_1 \otimes (M_2 \otimes M_3))$};

@@

(C) edge node [above] {$\lH(\alpha)$} (C')

@@

\node (A) at (0,0.5) {$F'(\alpha \kappa \kappa)(d_{(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)})$};
\node (B) at (0,-0.5) {$F'(\alpha \kappa)(d_{\lH(M_1 \otimes M_2) \otimes \lH(M_3)})$};
\node (C) at (0,-1.5) {$F'(\alpha)(d_{\lH((M_1 \otimes M_2) \otimes M_3)})$};
\node (A') at (5,0.5) {$F'(\kappa \kappa)(d_{\lH(M_1) \otimes (\lH(M_2) \otimes \lH(M_3))})$};
\node (B') at (5,-0.5) {$F'(\kappa)(d_{\lH(M_1) \otimes \lH(M_2 \otimes M_3)})$};
\node (C') at (5,-1.5) {$d_{\lH(M_1 \otimes (M_2 \otimes M_3))}$};

@@

where $$F'(\alpha \kappa \kappa)(d_{(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)}) = F'(\kappa \kappa \alpha')(d_{(\lH(M_1) \otimes \lH(M_2)) \otimes \lH(M_3)})$$
as the corresponding hexagon for the finite colimit preserving functor $H \maps \A \to \A'$ commutes. The map $\mu_{M_1,M_2}$ is also compatible with the braidings $\beta$ and $\beta'$ of $F \lCsp_1$ and $F' \lCsp_1$, respectively, and make the necessary square commute as a consequence of the corresponding commutative square involving braidings from the finite colimit preserving functor $H \maps \A \to \A'$.

We also have that the monoidal unit of $F\lCsp_1$ is given by:
\node (A) at (0,0) {$1_\A$};
\node (B) at (1,0) {$1_\A$};
\node (C) at (2,0) {$1_\A$};
\node (D) at (1,-0.5) {$!_{1_\A} \in F(1_\A)$};
(C) edge node[above]{$1$} (B);
where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\mathbb{H}$ is given by:
where $1_\A$ is the monoidal unit of the cocartesian category $\A$. The image of this horizontal 1-cell under $\lH$ is given by:
\node (A) at (0,0) {$H(1_\A)$};
\node (B) at (1,0) {$H(1_\A)$};
\node (C) at (2,0) {$H(1_\A)$};
%\node (E) at (3,0) {$=$};
%\node (F) at (4,0) {$1_\mathsf{A'}$};
%\node (G) at (5,0) {$1_\mathsf{A'}$};
%\node (H) at (6,0) {$1_\mathsf{A'}$};
%\node (I) at (5,-0.5) {$!_{1_{\mathsf{A'}}} \in F'(1_{\mathsf{A'}})$};
%\node (F) at (4,0) {$1_\A'$};
%\node (G) at (5,0) {$1_\A'$};
%\node (H) at (6,0) {$1_\A'$};
%\node (I) at (5,-0.5) {$!_{1_{\A'}} \in F'(1_{\A'})$};
\node (D) at (1,-0.5) {$\theta_{1_\A}E(!_{1_\A}) \phi \in F'(H(1_\A))$};
(C) edge node[above]{$1$} (B);
%(F) edge node[above]{$1$} (G)
%(H) edge node[above]{$1$} (G);
as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \mathbb{H}(1_{F\lCsp_1})$$ 
as $H$ preserves finite colimits. We then have a 2-isomorphism in $F'\lCsp$ given by: $$\mu \maps 1_{F'\lCsp_1} \to \lH(1_{F\lCsp_1})$$ 
\node (A) at (0,0.5) {$1_{\mathsf{A'}}$};
\node (A) at (0,0.5) {$1_{\A'}$};
\node (A') at (0,-0.5) {$H(1_\A)$};
\node (B) at (1.5,0.5) {$1_{\mathsf{A'}}$};
\node (C) at (3,0.5) {$1_{\mathsf{A'}}$};
\node (B) at (1.5,0.5) {$1_{\A'}$};
\node (C) at (3,0.5) {$1_{\A'}$};
\node (C') at (3,-0.5) {$H(1_\A)$};
\node (D) at (1.5,-0.5) {$H(1_\A)$};
\node (E) at (5,0.5) {$!_{1_\mathsf{A'}} \in F'(1_\mathsf{A'})$};
\node (E) at (5,0.5) {$!_{1_\A'} \in F'(1_\A')$};
\node (F) at (5,-0.5) {$\theta_{1_\A} E(!_{1_\A}) \phi \in F'(H(1_\A))$};
(C) edge node[right]{$\kappa$} (C')
together with the morphism $\tau_\mu \maps F'(\kappa)(!_{1_\mathsf{A'}}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F'(H(1_\A))$. The following square then commutes for any horizontal 1-cell $M$ of $F \lCsp$: 
together with the morphism $\tau_\mu \maps F'(\kappa)(!_{1_\A'}) \to (\theta_{1_\A} E(!_{1_\A})\phi)$ in $F'(H(1_\A))$. The following square then commutes for any horizontal 1-cell $M$ of $F \lCsp$: 
\node (A) at (0,0) {$1_\mathsf{A'} \otimes \mathbb{H}(M)$};
\node (B) at (2.5,0) {$\mathbb{H}(1_\A) \otimes \mathbb{H}(M)$};
\node (D) at (2.5,-1) {$\mathbb{H}(1_\A \otimes M)$};
\node (A) at (0,0) {$1_\A' \otimes \lH(M)$};
\node (B) at (2.5,0) {$\lH(1_\A) \otimes \lH(M)$};
\node (D) at (2.5,-1) {$\lH(1_\A \otimes M)$};
(A) edge node[above]{$\mu \otimes 1$} (B)
(A) edge node[left]{$\ell$} (C)
(B) edge node[right]{$\mu_{1_\mathrm{A},M}$} (D)
(D) edge node[above]{$\mathbb{H}(\ell')$} (C);
where we have abbreviated the monoidal units of $F\lCsp_1$ and $F'\lCsp_1$ as $1_\A$ and $1_\mathsf{A'}$, respectively. The diagram of corresponding decorations is given by:
\node (A) at (0,0.5) {$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$};
\node (B) at (0,-0.5) {$d_{\mathbb{H}(M)}$};
\node (A') at (4,0.5) {$F'(H(\ell') \kappa)(d_{!_{\mathbb{H}(1_\A)}}\otimes d_{\mathbb{H}(M)})$};
\node (B') at (4,-0.5) {$F'(H(\ell'))(d_{\mathbb{H}(1_\A \otimes M)})$};
(A) edge node[left]{$\tau_\ell$} (B)
(A) edge node[above]{$F'(H(\ell')\kappa)(\tau_{\mu \otimes 1})$} (A')
(A') edge node [right]{$F'(H(\ell'))(\tau_\kappa)$} (B')
(B') edge node [above] {$\tau_{H(\ell')}$} (B);
where $$F'(\ell)(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})=F'(H(\ell')\kappa(\mu \otimes 1))(d_{!_{1_\mathsf{A'}}} \otimes d_{\mathbb{H}(M)})$$ since the corresponding square involving left unitors for the finite colimit preserving functor $H \maps \A \to \mathsf{A'}$ commutes. The other square involving the right unitors $r$ and $r'$ is similar. Note that because the comparison constraints $\mu$ and $\mu_{(\_ , \_)}$ are both isomorphisms, the symmetric monoidal double functor $\mathbb{H}$ is strong.
